Fast and optimal centroiding of faint stars

### 2014-12-16 ms/figure.tex
Update figure.tex

We present a modification of the 3$\times$3 polynomial method for estimating the centroid 
of stars in astronomical images. After simulating a large number of stars with relatively low 
signal-to-noise-ratio, and in a wide range of full width at half maxima, we compare the results
of our method to those obtained from the quartic approximation method used in SDSS photometric pipeline, 
as well as finding the centroid by fitting the exact PSF model which was used to generate the 
simulated data. Comparison of the root-mean-squared error in centroid measurement, resulting 
from these techniques to the Cramer-Rao lower bound of centroid estimates, 
suggests that, the modified 3$\times$3 polynomial trick, though not as accurate as PSF fitting method
, is able to deliver results sufficiently close to the Cramer-Rao lower bound.

>>>>

One of the most demanding tasks in astronomical image processing is centroiding of stars. 
The upcoming large scale astronomical surveys are going to take images of billions of point sources, 
including many faint stars, in short exposure times. Thus, real-time accurate estimation of the
centroid of stars is crucial for further analysis of the photometric data such as PSF estimation,
and infering the proper motion of stars. In this work, we aim to compare the performances of
fast and profile-fitting centroiding methods when applied to relatively low signal-to-noise ratio
stars in a wide range of full width at half maxima.
Besides, in order to see how information preserving these techniques are, we compare
the root-mean-squared-error arising from these centroiding techniques with the Cramer-Rao
lower bound. The methods we discuss in this paper are: the naive 3$\times$3 polynomial centroiding,
a modification of this method, 3$\times$3 quartic approximation, and PSF profile fitting.
We find that 3$\times$3 modified polynomial cetroiding leads to
significant improvement in comparison with the naive polynomial centroiding, and gives rise
to centroiding errors comparable to those of 3$\times$3 quartic approximation method.
Moreover, our findings suggest that the 3$\times$3 modified polynomial, and the 3$\times$3
quartic approximation techniques, though not as accurate as PSF profile fitting methods,
are able to deliver results sufficiently close to saturating the Cramer-Rao lower bound in a range 
of relatively faint stars.
